Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-24 Ch1_movement_rates/Ch1_Figures.Rmd
Hmmm. I think my computer hates me now. I may need to give it a break. Working on density plots with thousands of lines.

ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

>>>>

#ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

## Figure Dispersal Kernels

```{r}
cp_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = "lightgray"))

pp_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = "lightgray"))

np_lines <- purrr::map(seq(1:1000), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = "lightgray"))

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[1], scale = CIs.cp.scale[1]), 
                color = "black", linetype = "dashed") +
  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[2], scale = CIs.cp.scale[2]), color = "black") +
  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[3], scale = CIs.cp.scale[3]),
                color = "black", linetype = "dashed") +
  lims(x = c(0, 1250)) +
  theme_bw() -> CPweibdens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[1], scale = CIs.pp.scale[1]), 
                color = "black", linetype = "dashed") +
  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[2], scale = CIs.pp.scale[2]), color = "black") +
  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[3], scale = CIs.pp.scale[3]),
                color = "black", linetype = "dashed") +
  lims(x = c(0, 1250)) +
  theme_bw() -> PPweibdens

ggplot() +
  np_lines +
  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[1], scale = CIs.np.scale[1]), 
                color = "black", linetype = "dashed") +
  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[2], scale = CIs.np.scale[2]), color = "black") +
  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[3], scale = CIs.np.scale[3]),
                color = "black", linetype = "dashed") +
  lims(x = c(0, 1250)) +
  theme_bw() -> NPweibdens

plot_grid(CPweibdens, PPweibdens, NPweibdens, nrow = 3)
